Initial Analysis

### 2019-11-29 Initial_Analysis.Rmd
Completed Figure one with circular regional contributions

  theme(text             = element_text(#family = "Helvetica",
    color = "gray30", size = base_size),
    plot.title       = element_text(size = rel(1.25), hjust = 0, face = "bold"),
    panel.background = element_blank(),
    panel.border     = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(color = "transparent"),
    strip.background =element_rect(fill = "transparent"),
    strip.text.x = element_text(size = 18, colour = "black",face= "bold.italic", angle = 0),
    axis.line        = element_blank(), # element_line(colour = "grey30", size = .5))
    axis.ticks       = element_blank(),
    axis.text        = element_blank(),
    axis.title       = element_blank(),
    legend.key       = element_rect(colour = NA, fill = NA, size = 4),
    legend.position = "bottom",
    legend.key.width =unit(6,"line")
  )
}

@@

## Create Transboundary Catch Database

@@

@@

```{r catch, eval = F, echo = T}
# Notes, needs GetSppDist
# Note, It averages the LAST 10 years oe ach gridcell and then adds them together

@@

# Read Sau Catch Data
# SAU_Catch_Data <- fread(paste(Data_Path,"Distribution_Data/Sau_Catch_Data.csv", sep ="")) %>% 
  # filter(!is.na(Territory))

@@

@@

# Get Catch data for mapping (Currently not used)

# Catch_Country <- Sau_Catch_Data %>% 
#   group_by(FishingRegion=Territory) %>% 
#   summarise(Total_Catch = round(sum(Mean_Catch,na.rm=T),2)) %>% 
#   filter(!(is.na(FishingRegion))) %>% 
#   left_join(Clean_sau_eez_fes) %>% 
#   group_by(Territory = fishing_entity) %>% 
#   summarise(Total_Catch = sum(Total_Catch,na.rm=T)) %>% 
#   mutate(Territory = gsub("USA","United States of America",Territory))

@@

Continent_Data <- Revenue_Country %>% 
  left_join(UN_Regions,
            by = "fishing_entity") %>% 
  mutate(sub_region = ifelse(is.na(sub_region), "Other",paste(sub_region))) %>% 
  group_by(sub_region) %>% 
  summarise_if(is.numeric,sum,na.rm=T)

@@

@@

label_data <- Continent_Data_Trans %>% 
  arrange(Total_USD) %>% # soo it looks like a nice snail :)
  mutate(
    id = seq(1,nrow(Continent_Data_Trans)),
    angle = 90 -360 * (id-0.5)/number_of_bar,
    hjust = ifelse(angle < -90,1,0),
    angleb = ifelse(angle < -90, (angle +180), angle)
  ) %>% 
  mutate(
    sub_region = ifelse(str_detect(sub_region,"Latin"),"Latin America &\nthe Caribbean",
                        ifelse(sub_region =="Northern America","Northern\nAmerica",
                        paste(sub_region))
    )
  )

@@

@@

# Make map
Map <- ggplot() +
  geom_sf(data = World_sf_si_land,aes(fill = reorder(Bins_Plot,Total_USD)), colour = "grey80",size = 0.1) +
  geom_sf(data = World_sf_si,aes(fill =  reorder(Bins_Plot,n_trans_spp)),colour = "grey20", size = 0.1) + # n_trans_spp or Bins
  geom_sf(data = Grey_land,aes(fill = Bins),fill = "grey80", colour = "grey50",size = 0.1) + # n_trans_spp or Bins
  # scale_fill_gradientn(colours = pal,
  #                      na.value = "white") +
  # scale_fill_manual(values = c(rev(wes_palette(n = 4, name = "Darjeeling1")),
  # rev(wes_palette(n = 4, name = "Darjeeling2"))
  # ),
  # na.value = "white"
  # ) +
  scale_fill_manual("",values = c("#5BBCD6",#"#5BBCD6", # blue
                                  "#00A08A",#"#00A08A", #green
                                  "#F2AD00",#"#F2AD00", # Yellow
                                  # "#F98400",#"#F98400", #Orange
                                  "#FF0000"#,"#FF0000" #Red
  ),
  na.value = "white"
  ) +
  # scale_fill_manual(values = rev(wes_palette(n = 5, name = "Darjeeling1")),
  #                    na.value = "white"
  # ) +
  ggtheme_map()

@@

# Revenue Plot
# Set plot limits
min_lim <- min(Continent_Data_Trans$Total_USD)
max_lim <-max(Continent_Data_Trans$Total_USD)

@@

Rev_Plot <- ggplot(data = Continent_Data_Trans, 
       aes(x=reorder(id,Total_USD),
           y=Total_USD, 
           fill=Total_USD
           )
       ) +    
  ylim(-1500, max_lim+10)+
  geom_bar(stat="identity") +
  theme_minimal() +
  theme(
    # legend.position = c(0.80,0.50),
    legend.position = "",
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = margin(0,-10,-5,-10,"cm")
  )  +
  # Base line
  geom_segment(aes(x = 1, y = 1, xend = 17, yend = 17),  
               colour = "black", size=0.1, inherit.aes = FALSE) +
  coord_polar(start = 0) + 
  geom_text(data=label_data, 
            aes(x=id,
                y=Total_USD+10,
                # label=round(Total_USD_Billion),
                label=sub_region,
                hjust=hjust), 
            color="black",
            fontface="bold",
            size=2, 
            angle= label_data$angleb, 
            inherit.aes = FALSE) +
  scale_fill_gradientn("Billion USD",
                       colours = pal)

@@

Catch_Plot <- ggplot(data = Continent_Data_Trans, 
       aes(x=reorder(id,Total_USD),
           y=Total_USD, 
           fill=Total_USD
           )
       ) +    
  ylim(-1500, max_lim+10)+
  geom_bar(stat="identity") +
  theme_minimal() +
  theme(
    # legend.position = c(0.80,0.50),
    legend.position = "",
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = margin(0,-10,-5,-10,"cm")
  )  +
  # Base line
  geom_segment(aes(x = 1, y = 1, xend = 17, yend = 17),  
               colour = "black", size=0.1, inherit.aes = FALSE) +
  coord_polar(start = 0) + 
  geom_text(data=label_data, 
            aes(x=id,
                y=Total_USD+10,
                # label=round(Total_USD_Billion),
                label=sub_region,
                hjust=hjust), 
            color="black",
            fontface="bold",
            size=2, 
            angle= label_data$angleb, 
            inherit.aes = FALSE) +
  scale_fill_gradientn("Tons",
                       colours = pal)

@@

plot <- ggdraw() +
  # map
  draw_plot(Map, x = 0, y = 0.4, width = 1, height = 0.6) +
  # Revenue circular
  draw_plot(Rev_Plot, x = 0.1, y = 0.1, width = 0.5, height = 0.4) +
  # Catch circular
  draw_plot(Catch_Plot, x = 0.45, y = 0.1, width = 0.5, height = 0.4) +

  # Labeks
  draw_plot_label(label = c("A", "B", "C"), 
                  size = 30,
                  x = c(0.1, 0.1, 0.5), 
                  y = c(1, 0.45, 0.45)
  )

# Plot_Name <- paste("100_25_Bins_Value_Region.png", sep = "")

save_plot("Plot.png",
          plot,
          base_height = 8,
          base_width = 13)

ggsave(Plot_Name,
       plot = Plot,
       width = 16,
       height = 8,
       units = "in",
       path = Figures_Path
)

>>>>

  theme(text             = element_text(#family = "Helvetica",
    color = "gray30", size = base_size),
    plot.title       = element_text(size = rel(1.25), hjust = 0, face = "bold"),
    panel.background = element_blank(),
    panel.border     = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(color = "transparent"),
    strip.background =element_rect(fill = "transparent"),
    strip.text.x = element_text(size = 18, colour = "black",face= "bold.italic", angle = 0),
    axis.line        = element_blank(), # element_line(colour = "grey30", size = .5))
    axis.ticks       = element_blank(),
    axis.text        = element_blank(),
    axis.title       = element_blank(),
    legend.key       = element_rect(colour = NA, fill = NA, size = 4),
    legend.position = "bottom",
    legend.key.width =unit(5,"line")
  )
}

@@

## Get Catch Data

@@

### Sub routine for catch data

@@

```{r subroutine_get_catch_data, eval = F, echo = T}
# Notes, needs GetSppDist
# Note, It averages the LAST 10 years oe ach gridcell and then adds them together

@@

# Read Sau Catch Data
SAU_Catch_Data <- fread(paste(Data_Path,"Distribution_Data/sau_catch_country_taxon.csv", sep =""))

@@

# -------------------------- #
# Total Catch
# -------------------------- #

Total_Trans_Catch <- SAU_Catch_Data %>% 
  filter(taxon_key %in% Total_trans$taxon_key) %>% 
  group_by() %>% 
  summarise(Total =sum(total_catch)/1000000) %>%  # total revenue within EEZs of the world from sau.org
  pull()

Global_Catch <- 108 # million (estimated from sau.com)

Per_Catch <- (Total_Trans_Catch/Global_Catch)*100

@@

# Get Catch data for mapping (Supplemental materials)

Catch_Country <- SAU_Catch_Data_b %>%
  group_by(eez_name) %>%
  summarise(eez_catch = round(sum(total_catch,na.rm=T),2)) %>%
  left_join(Clean_sau_eez_fes,
            by = "eez_name") %>%
  group_by(fishing_entity) %>%
  summarise(fishing_entity_catch = sum(eez_catch,na.rm=T)/1000000) %>% # Million
  mutate(fishing_entity = ifelse(fishing_entity == "USA","United States of America",
                                 ifelse(fishing_entity == "Russian Federation","Russia",fishing_entity)),
         Bins = cut(fishing_entity_catch,breaks = 4),
         Bins_Plot = cut(fishing_entity_catch,breaks = 4,
                         labels = c('super low', 'low','high','super high'))
  ) %>% 
  filter(fishing_entity_catch > 0)

@@

### Catch Data

# Catch_Country

### Revenue Data
Continent_Data <- Revenue_Country %>% 
  left_join(Catch_Country,
             by = "fishing_entity") %>% 
  left_join(UN_Regions,
            by = "fishing_entity") %>% 
  mutate(sub_region = ifelse(is.na(sub_region), "Other",paste(sub_region))) %>% 
  group_by(sub_region) %>% 
  summarise_if(is.numeric,sum,na.rm=T)

@@

# Fix names for plot
Continent_Data_Trans$sub_region <- Continent_Data_Trans$sub_region %>% 
  gsub("Northern","N.",.) %>% 
  gsub("Southern","S.",.) %>% 
  gsub("Western","W.",.) %>% 
  gsub("Eastern","E.",.)

@@

label_data_rev <- Continent_Data_Trans %>% 
  arrange(Total_USD) %>% # soo it looks like a nice snail :)
  mutate(
    id = seq(1,nrow(Continent_Data_Trans)),
    angle = 90 -360 * (id-0.5)/number_of_bar,
    hjust = ifelse(angle < -90,1,0),
    angleb = ifelse(angle < -90, (angle +180), angle)
  ) %>% 
  mutate(
    sub_region = ifelse(str_detect(sub_region,"Latin"),"Ltn. Ame. &\nthe Car.",
                        ifelse(sub_region =="Northern America","Northern\nAmerica",
                               paste(sub_region))
    )
  )

label_data_catch <- Continent_Data_Trans %>% 
  arrange(fishing_entity_catch) %>% # soo it looks like a nice snail :)
  mutate(
    id = seq(1,nrow(Continent_Data_Trans)),
    angle = 90 -360 * (id-0.5)/number_of_bar,
    hjust = ifelse(angle < -90,1,0),
    angleb = ifelse(angle < -90, (angle +180), angle)
  ) %>% 
  mutate(
    sub_region = ifelse(str_detect(sub_region,"Latin"),"Ltn. Ame. &\nthe Car.",
                        ifelse(sub_region =="Northern America","Northern\nAmerica",
                               paste(sub_region))
    )
  )

@@

```{r Territory_Map_Round, eval =F, echo =F}

@@

# Create labels for legend
Labels_Trans <- c(paste(unique(Transboundary_Spp$Bins)),"NA")
Labels_Rev <- unique(Revenue_Country$Bins)

# Make map
Map <- ggplot() +
  geom_sf(data = World_sf_si_land,aes(fill = reorder(Bins_Plot,Total_USD)), colour = "grey80",size = 0.1) +
  geom_sf(data = World_sf_si,aes(fill =  reorder(Bins_Plot,n_trans_spp)),colour = "grey20", size = 0.1) + # n_trans_spp or Bins
  geom_sf(data = Grey_land,aes(fill = Bins),fill = "grey80", colour = "grey50",size = 0.1) + # n_trans_spp or Bins
  # scale_fill_gradientn(colours = pal,
  #                      na.value = "white") +
  # scale_fill_manual(values = c(rev(wes_palette(n = 4, name = "Darjeeling1")),
  # rev(wes_palette(n = 4, name = "Darjeeling2"))
  # ),
  # na.value = "white"
  # ) +
  scale_fill_manual("",values = c("#5BBCD6",#"#5BBCD6", # blue
                                  "#00A08A",#"#00A08A", #green
                                  "#F2AD00",#"#F2AD00", # Yellow
                                  # "#F98400",#"#F98400", #Orange
                                  "#FF0000"#,"#FF0000" #Red
  ),
  na.value = "white"
  ) +
  # scale_fill_manual(values = rev(wes_palette(n = 5, name = "Darjeeling1")),
  #                    na.value = "white"
  # ) +
  ggtheme_map() +
  # Transboundary labels
  annotate("text", 
           x =(c(-95,-36,21,80,146)+4),
           y = -93.5,
           label = Labels_Trans, 
           color="black", 
           size=3, 
           angle=0, 
           # fontface="bold",
           hjust=0) +
  # Revenue labels
  annotate("text", 
           x =c(-100,-48,12,69),
           y = -110,
           label = Labels_Rev, 
           color="black", 
           size=3, 
           angle=0, 
           # fontface="bold",
           hjust=0) +
  # Legend Titles
  annotate("text", 
           x =-190,
           y = -93.5,
           label = "Transboundary Spp. (n)", 
           color="black", 
           size=3, 
           angle=0, 
           fontface="bold",
           hjust=0) +
  annotate("text", 
           x =-190,
           y = -110,
           label = "Revenue (Million USD)", 
           color="black", 
           size=3, 
           angle=0, 
           fontface="bold",
           hjust=0) +
  theme(
    legend.box.margin = margin(t = -54, l = 130),
    legend.text = element_blank()#,
  )

# Map

@@

# Revenue Plot
# Set plot limits
max_lim <- max(Continent_Data_Trans$Total_USD)

@@

Rev_Plot <- ggplot(data = Continent_Data_Trans, 
                   aes(x=reorder(id,Total_USD),
                       y=Total_USD, 
                       fill=Total_USD
                   )
) +    
  ylim(-1500, max_lim+10)+
  geom_bar(stat="identity") +
  theme_minimal() +
  theme(
    legend.position = c(0.74,0.60),
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = margin(0,-10,-6,-10,"cm")
  )  +
  # Base line
  geom_segment(aes(x = 1, y = 1, xend = 17, yend = 17),  
               colour = "black", size=0.1, inherit.aes = FALSE) +
  coord_polar(start = 0) + 
  geom_text(data=label_data_rev, 
            aes(x=id,
                y=Total_USD+10,
                # label=round(Total_USD_Billion),
                label=sub_region,
                hjust=hjust), 
            color="black",
            fontface="bold",
            size=2, 
            angle= label_data$angleb, 
            inherit.aes = FALSE) +
  scale_fill_gradientn("",
                       colours = pal) +
  guides(fill = guide_colorbar(label.position = "left")
  )

@@

max_lim <- max(Continent_Data_Trans$fishing_entity_catch)

Catch_Plot <- ggplot(data = Continent_Data_Trans, 
                     aes(x=reorder(id,fishing_entity_catch),
                         y=fishing_entity_catch, 
                         fill=fishing_entity_catch
                     )
) +    
  ylim(-1.5, max_lim+1) +
  geom_bar(stat="identity") +
  theme_minimal() +
  theme(
    legend.position = c(0.1,0.60),
    # legend.position = "right",
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = margin(0,-10,-6,-5,"cm")
    # plot.margin = margin(0,0,-5,0,"cm")
  )  +
  # Base line
  geom_segment(aes(x = 0, y = 1, xend = 17, yend = 17),
               colour = "black", size=0.1, inherit.aes = FALSE) +
  coord_polar(start = 0) + 
  geom_text(data=label_data_catch, 
            aes(x=id,
                y=fishing_entity_catch+0.1,
                # label=round(Total_USD_Billion),
                label=sub_region,
                hjust=hjust), 
            color="black",
            fontface="bold",
            size=2, 
            angle= label_data$angleb, 
            inherit.aes = FALSE) +
  scale_fill_gradientn("",
                       colours = pal)

# Catch_Plot

@@

plot <- ggdraw() +
  # map
  draw_plot(Map, x = 0, y = 0.45, width = 1, height = 0.58) +
  # Revenue circular
  draw_plot(Rev_Plot, x = 0.1, y = 0.07, width = 0.5, height = 0.4) +
  # Catch circular
  draw_plot(Catch_Plot, x = 0.45, y = 0.07, width = 0.5, height = 0.4) +

  # Labeks
  draw_plot_label(label = c("A", "B"), 
                  size = 20,
                  x = c(0, 0), 
                  y = c(1, 0.45)
  ) +
  draw_plot_label(label = c("Revenue (USD) | Catch (Tones)","(Million)"), 
                  size = 8,
                  x = c(0.333,0.493), 
                  y = c(0.30,0.28)
  )

save_plot(paste(Figures_Path,"100_25_Bins_Value_Region.png",sep=""),
          plot,
          base_height = 8,
          base_width = 8)
